A Step-Indexed Logic in Agda

### 2023-06-23 papers/cpp2024/paper.tex
check

\usepackage{newunicodechar}
\newunicodechar{λ}{\ensuremath{\mathnormal\lambda}}
\newunicodechar{←}{\ensuremath{\mathnormal\from}}
\newunicodechar{→}{\ensuremath{\mathnormal\to}}
\newunicodechar{∀}{\ensuremath{\mathnormal\forall}}
\newunicodechar{∃}{\ensuremath{\exists}}
\newunicodechar{⊥}{\ensuremath{\mathnormal\bot}}
\newunicodechar{⊤}{\ensuremath{\mathnormal\top}}
\newunicodechar{∷}{\ensuremath{\mathnormal::}}
\newunicodechar{ℕ}{\ensuremath{\mathbb N}}
\newunicodechar{≤}{\ensuremath{\leq}}
\newunicodechar{∸}{\ensuremath{\div}}
\newunicodechar{′}{\ensuremath{'}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{₁}{\ensuremath{_1}}
\newunicodechar{₂}{\ensuremath{_2}}
\newunicodechar{Σ}{\ensuremath{\Sigma}}
\newunicodechar{⊎}{\ensuremath{\cupdot}}
\newunicodechar{ᵖ}{\ensuremath{^p}}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{≢}{\ensuremath{\not\equiv}}
\newunicodechar{∘}{\ensuremath{\circ}}
\newunicodechar{ᵒ}{\ensuremath{^\circ}}
\newunicodechar{▷}{\ensuremath{\rhd}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Step-indexed logical relations are an important tool in the
  metatheory of programming
  languages~\citep{Appel:2001aa,Ahmed:2006aa}, and their application
  can be streamlined by use of modal logics such as
  LSLR~\citep{Dreyer:2011wl}.  The Iris system~\citep{JUNG:2018aa}
  provides support for reasoning about step-indexed logical relations
  in the Coq proof assistant, but there is not yet analogous support
  for the Agda proof assistant. This paper describes an embedding of
  a step-indexed logic in Agda and an application of the logic to a
  semantic type safety proof for an internal language for the
  Gradually-Typed Lambda Calculus.
\end{abstract}

@@

%TODO: ROAD MAP

>>>>

\usepackage{newunicodechar}
\newunicodechar{λ}{\ensuremath{\mathnormal\lambda}}
\newunicodechar{←}{\ensuremath{\mathnormal\from}}
\newunicodechar{→}{\ensuremath{\mathnormal\to}}
\newunicodechar{↓}{\ensuremath{\mathnormal\downarrow}}
\newunicodechar{∀}{\ensuremath{\mathnormal\forall}}
\newunicodechar{∃}{\ensuremath{\exists}}
\newunicodechar{⊥}{\ensuremath{\mathnormal\bot}}
\newunicodechar{⊤}{\ensuremath{\mathnormal\top}}
\newunicodechar{∷}{\ensuremath{\mathnormal::}}
\newunicodechar{ℕ}{\ensuremath{\mathbb N}}
\newunicodechar{≤}{\ensuremath{\leq}}
\newunicodechar{∸}{\ensuremath{\div}}
\newunicodechar{′}{\ensuremath{'}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{₁}{\ensuremath{_1}}
\newunicodechar{₂}{\ensuremath{_2}}
\newunicodechar{Σ}{\ensuremath{\Sigma}}
\newunicodechar{⊎}{\ensuremath{\cupdot}}
\newunicodechar{ᵖ}{\ensuremath{^p}}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{≢}{\ensuremath{\not\equiv}}
\newunicodechar{∘}{\ensuremath{\circ}}
\newunicodechar{ᵒ}{\ensuremath{^\circ}}
\newunicodechar{▷}{\ensuremath{\rhd}}
\newunicodechar{∈}{\ensuremath{\in}}
\newunicodechar{⇔}{\ensuremath{\iff}}
\newunicodechar{⩦}{\ensuremath{\equiv}} % !!
\newunicodechar{μ}{\ensuremath{\mu}}
\newunicodechar{∋}{\ensuremath{\ni}}
\newunicodechar{ˢ}{\ensuremath{^s}}
\newunicodechar{ᵈ}{\ensuremath{^d}}
\newunicodechar{Γ}{\ensuremath{\Gamma}}
\newunicodechar{∅}{\ensuremath{\emptyset}}
\newunicodechar{δ}{\ensuremath{\delta}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Step-indexed logical relations are an important tool in the
  metatheory of programming
  languages~\citep{Appel:2001aa,Ahmed:2006aa}, and their application
  can be streamlined by use of modal logics such as
  LSLR~\citep{Dreyer:2011wl}.  The Iris system~\citep{JUNG:2018aa}
  provides support for reasoning about step-indexed logical relations
  in the Coq proof assistant. This paper describes a shallow embedding
  of a step-indexed logic in Agda and its application to a semantic
  type safety proof for an internal language of the Gradually-Typed
  Lambda Calculus.
\end{abstract}

@@

TODO: ROAD MAP
